# Setting up the experiment {#sec-setup .unnumbered}

This section explains the experimental method in detail. Please follow the instructions as closely as possible, and report any deviations from the protocol using the <a href="https://docs.google.com/forms/d/e/1FAIpQLSfXoKjJo3XgGuXCLhWhzEDz0UrJ7tmio-70SoS24g4vqc4Utg/viewform?usp=sf_link" target="_blank"><b>MB5 issue tracker form</b></a>.

-   @sec-participants
-   @sec-stimuli
-   @sec-procedure
-   @sec-apparatus
-   @sec-validation

```{=html}
<!-- 
Each baby will be presented with a series of 12 trials with one familiarization and two test phases each. During familiarization, a single stimulus is presented centrally on the screen. The test phase will consist of two stimuli, one familiar and one novel, presented side-by-side. The location of the stimuli will be switched in the two test trials. The duration of the familiarization will vary across trials (5, 10, or 15s). The tests will last 5s each. There will be two versions of the experiment: one in which the familiarization time will be pre-established (*fixed-length*), and another one in which the length of the trial will last until the infant accumulates the required looking time (*infant-controlled*). 
-->
```

````{=html}
<!-- leaving this in from template for now, so we know how to add figs and tables 

Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.

See Figure \@ref(fig:nice-fig).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

-->
````
